Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-08-01 sections/approach.tex
moved the footnote to the end of paragraph

\textbf{Definition:} We define a \emph{useful} comment as one that contributes to improving the proposed change, and a \emph{useless}\footnote{Although we call these comments \emph{useless} in our study, it might actually be useful---or sometimes even required---in some other contexts, such as to facilitate communication or to enforce guidelines.} comment as one that does not.

>>>>

\textbf{Definition:} We define a \emph{useful} comment as one that contributes to improving the proposed change, and a \emph{useless} comment as one that does not\footnote{Although we call these comments \emph{useless} in our study, it might actually be useful---or sometimes even required---in some other contexts, such as to facilitate communication or to enforce guidelines.}.
